Develop atlantisom wrappers

### 2020-01-16 WrapperDevelopment.Rmd
wrapper for survey and fishery index in progress

om_index <- function(){

@@

#CC3om_sard_ind <- om_index(c("survey1", "fishery"), CC3om_sardine)

>>>>

om_index <- function(surveyconfig = survey_configfile, 
                     fisheryconfig = fishery_configfile, 
                     omlist_ss = omlist_ss, 
                     n_reps = n_reps,
                     save = TRUE){

  #configure the independent survey, a default census is in config/survcensus.R
  #survey configuration must specify survey time, area, efficiency (q), selectivity
  #survey species inherited from omlist_ss
  source(surveyconfig)

  #biomass based fishery independent survey index
  # this uses result$biomass_ages to sample biomass directly, no need for wt@age est
  survey_B <- atlantisom::create_survey(dat = omlist_ss$truebio_ss,
                                        time = survtime,
                                        species = survspp,
                                        boxes = survboxes,
                                        effic = surveffic,
                                        selex = survselex)

  # call sample_survey_biomass with a bunch of 1000s for weight at age
  # in the code it multiplies atoutput by wtatage/1000 so this allows us to use
  # biomass directly
  wtage <- data.frame(species=rep(survspp, each=max(age_classes)),
                      agecl=rep(c(1:max(age_classes)),length(survspp)),
                      wtAtAge=rep(1000.0,length(survspp)*max(age_classes)))

  # this is the step to repeat n_reps time if we want different realizations 
  # of the same survey design specified above; only observation error differs
  # using the census cv of 0 will produce identical reps!
  survObsBiomB <- list()
  for(i in 1:n_reps){
    survObsBiomB[[i]] <- atlantisom::sample_survey_biomass(survey_B, surv_cv, wtage)
  }

  #save survey indices, takes a long time to generate with lots of reps/species
  if(save){
    saveRDS(survObsBiomB, file.path(d.name, paste0(scenario.name, "surveyB.rds")))
  }

  #configure the fishery, a default is in config/fisherycensus.R
  #fishery configuration must specify survey time, area, efficiency (q), selectivity
  #fishery species inherited from omlist_ss
  source(fisheryconfig)

@@

CC3om_sard_ind <- om_index(surveyconfig = here("config/survcensus.R"), 
                           fisheryconfig = "",
                           omlist_ss = CC3om_sardine, 
                           n_reps = 5, 
                           save = FALSE)
